Data Preparation, Integration and Cleaning

### 2017-02-06 abbDataPrep_Script.Rmd
adding clean counting objects

  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, 
       beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
       suburbs.shp, study.suburbs,
       file=paste0(data.path, 'prepared/prep_workspace.RData'))

>>>>

  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, 
       beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
       suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
       ltr.run.total, str.run.total,
       file=paste0(data.path, 'prepared/prep_workspace.RData'))
